Ignition of Fuel Beds by Firebrands

### 2022-04-14 manuscript3.tex
Finished the species paper results up to CFD.

@@

    Comparing the ignition trends of oak wood to the non ignition of pine bark and douglas-fir bark it would seem that a potential cause of decreased ignition is correlated to the material properties. Density particle size chemistry

    In summary, characterizing the flaming ignition propensity of fuels with respect to chemical composition alone will likely not yield satisfactory results. The inclusion of other material properties, such as thermal conductivity, however, may add enough additional knowledge for comprehensive predictions of ignition to be made. Further investigation of the differences in chemical and thermal properties of the materials is necessary to unravel the interactions between thermal and chemical processes and the resulting impact on flaming ignition before knowledge sufficient for a predictive tool that may be used for fire prevention and management may be created
    \cite{MacLean1941}.

>>>>

    Taking into account the consistent ignition heat source and environmental conditions the remaining differences that may be driving factors for ignition trends are material properties. 
    The easiest material property to quantify and compare is the bulk density of the materials. However, there is no clear correlation between density and probability of ignition. Consider first the wheat straw, which was not observed to ignite at either wind speed, had a bulk density between that of pine wood and Douglas-fir wood which ignited in both wind conditions. Based on bulk density wheat straw would be anticipated to ignite at a temperature between these two materials. Similarly, oak wood has a bulk density higher than that of the douglas-fir bark and pine bark but was observed to ignite in the low wind speed cases. Clearly bulk density of the material is not a sufficient to differentiation between cases where ignition does or does not occur leaving differences in chemical composition as the remaining predictor.

@@

    In an effort to elucidate the effects of pyrolysis on ignition propensity modelling was conducted.

    \section{Conclusions}
    \cite{MacLean1941}.
